Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
horrible design storywriting.

\section{Design}
\#STORYTIMEE  about why we chose this experiment.

Design of experiment.

Methodology of experiment.

What we hope to get from this experiment

>>>>

\section{Design}
After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc. But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention. To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.

For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary {\color {red} is this true?.. or what happens?} We will them instruct them to complete the set of tasks. We designed the experiment so that the users are able to complete some easy tasks without having to use a censorship circumvention tool. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.

{\color {red} might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study. This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley. The laboratory space consists of 36 Toshiba Tecra R850 laptops in 6 rows of 6 laptops each, with cubicle walls separating each laptop. We used individual host firewalls to simulate the censorship environments. We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit. The total length of the experiment should be less than an hour. Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.

We plan to analyze: which configuration tasks are hard (bridges vs proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
